%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://jameslimer.com/}{\Large Yiming Lin}} & Email : \href{mailto:yiming.lin17@xjtlu.edu.cn}{yiming.lin17@xjtlu.edu.cn}\\
  \href{http://www.jameslimer.com/}{http://www.jameslimer.com} & Mobile : +86-180-1261-7703 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Xi'an Jiaotong-Liverpool University}{SuZhou, China}
      {Information and Computer Science - Overall GPA: 3.62/4.000, Major GPA: 3.98/4.000}{Aug. 2017 -- Now}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {XJTLU-Hackthon 2018}{SuZhou, China}
      {First Prize}{Jun 2018}
      \resumeItemListStart
        \resumeItem{Optical Music-Sheet Recognition}
          {\\Created an Automatic Piano which, through image recognition, can play piano scores.\\
      The product won the first prize and received a reward of RMB 5,000 in cash.}
      \resumeItemListEnd

    \resumeSubheading
      {Sensys 2018 Conference Paper}{ShenZhen, China}
      {Co-auther of "Ecrt: An edge computing system for real-time image-based object tracking"}{Aug 2018 - Jun 2019}

      \resumeItemListStart
       \resumeItem{Attended Sensys 2018 Conference}{ }
        \resumeItem{Edge Computing, Deep Learning and Reinforcement Learning}
          {\\Designed an Edge Computing system for Real-time object Tracking (ECRT) for resource-constrained devices.\\
          The key feature of the system is that it intelligently partitions compute-intensive tasks such as inferencing a convolutional neural network (CNN) into two parts, which are executed locally on an IoT device and/or on the edge server.\\
          In the later version, instead of using heuristic algorithm we designed a Reinforcement learning algorithm to scheduling the partition points, the later version is in submission.}
      \resumeItemListEnd

    \resumeSubheading
      {Summer Undergraduate Research Fellowships 2018}{SuZhou, China}
      {Author of "Object Tracking via Deep Neural Networks Using Dynamic Template Module"}{Summer 2019}
      \resumeItemListStart
        \resumeItem{Video Object Tracking}
          {\\Designed a LSTM-based Dynamic Template Module to improve robustness of current Siamese-neuron-network based tracking model.}
        \resumeItem{Video Prediction Framework}
          {\\Also developed a Video Prediction Framework Framework based on pytorch.}
      \resumeItemListEnd

    \resumeSubheading
      {Computer association in XJTLU}{SuZhou, China}
      {Vice President of the association}{Jan 2018 - Now}
     
    \resumeSubheading
      {Research Assistant - Machine Learning in XJTLU}{SuZhou, China}
      {Research Assistant of PremiLab@XJTLU}{July 2018 - Now}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{QuantSoftware Toolkit}
      {Open source python library for financial data analysis and machine learning for finance.}
    \resumeSubItem{Github Visualization}
      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
    \resumeSubItem{Recommendation System}
      {Music and Movie recommender systems using collaborative filtering on public datasets.}
    \resumeSubItem{Mac Setup}
      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
